---
title: "Chapter 7 Problem 6"
author: "Andira Putri"
output: pdf_document
---

In this exercise, you will further analyze the `Wage` data set considered throughout this chapter.

#### a. Perform polynomial regression to predict wage using age. Use cross-validation to select the optimal degree d for the polynomial. What degree was chosen, and how does this compare to the results of hypothesis testing using ANOVA? Make a plot of the resulting polynomial fit to the data.

```{r}
set.seed(1)
library(ISLR)
data(Wage)

#perform polynomial regression up to degree 5
fit.1=lm(wage~age ,data=Wage) #linear
fit.2=lm(wage~poly(age,2),data=Wage) #quadratic  
fit.3=lm(wage~poly(age,3),data=Wage) #cubic
fit.4=lm(wage~poly(age,4),data=Wage) #quartic
fit.5=lm(wage~poly(age,5),data=Wage) #quintic
anova(fit.1,fit.2,fit.3,fit.4,fit.5)
```

The linear and quadratic models are not sufficient because their p-values are close to 0. The quintic model has a rather high p-value at 0.37. The ANOVA table suggests that the cubic and quartic models are the best ones. Now, let's use cross-validation methods to pick the best among those two...

```{r}
set.seed(1)
library(ISLR)
library(boot)
cv=rep(0,5)

for (i in 1:5) {
  fit=glm(wage~poly(age,i),data=Wage)
  cv[i]=cv.glm(Wage,fit,K=5)$delta
}

plot(cv,type="b")
```

Cross-validation supports that the fourth-degree polynomial has the lowest estimated error.

From both the ANOVA table and CV, we conclude that the quartic model is the best one.

```{r}
#Resulting plot
library(ISLR)
agelims=range(Wage$age)
age.grid=seq(from=agelims[1],to=agelims[2])
preds=predict(fit,newdata=list(age=age.grid),se=TRUE)
plot(Wage$age,Wage$wage,xlim=agelims,cex=0.5,col="darkgrey")
title("Degree 4 Polynomial Fit")
lines(age.grid,preds$fit,lwd=2,col="red")

```

#### b. Fit a step function to predict wage using age, and perform cross validation to choose the optimal number of cuts. Make a plot of the fit obtained.

```{r}
set.seed(1)
library(ISLR)
data(Wage)
cv = rep(0,9)
for (i in 2:15) {
  Wage$age.cut=cut(Wage$age,i)
  step=glm(wage~age.cut,data=Wage)
  cv[i-1]=cv.glm(Wage,step,K=5)$delta[1]
}
cv
plot(2:15, cv, type="b",xlab="Number of Cuts")
```


With the plot, it seems like 8 is the best number of cuts.

```{r}
#Step Function Plot
cut=glm(wage~cut(age,8), data=Wage)
preds=predict(cut, newdata=list(age=age.grid), se=TRUE)
plot(Wage$age, Wage$wage, xlim=agelims, cex=0.5, col="darkgrey")
lines(age.grid, preds$fit, lwd=2, col="red")
```