---
title: "Chapter 5 Problem 9"
author: "Andira Putri"
output: pdf_document
---

#### We will now consider the `Boston` housing data set from the `MASS` library.

```{r}
set.seed(1)
library(MASS)
data(Boston)
```

#### a. Based on the data set, provide an estimate for the population mean of `medv`.
We shall call this population mean $\hat{\mu}$.

```{r}
pop.mean<-mean(Boston$medv)
pop.mean #mu hat
```

#### b. Provide an estimate of the standard error of the population mean. Interpret the result.

Standard error is given by $\sigma=\frac{\sigma_{medv}}{\sqrt{n}}$, where $\sigma_{medv}$ is the standard deviation of the population.

```{r}
pop.se<-sd(Boston$medv)/sqrt(length(Boston$medv))
pop.se
```

Our sample means vary from our population mean by 40.89%.

#### c. Now estimate the standard error of the population mean using the bootstrap. How does this compare to your answer from part (b)?

The bootstrap is an iterative cross-validation method that allows us to emulate the process of obtaining new sample sets so that we can estimate a quantity of a population, like mean and standard error. Basically, you are resampling a data set with replacement. When generating sample sets, bootstrap randomly takes observations from big data sets one at a time, and then it returns that point back to the data set so that it can be used in an estimation again.

Bootstrap algorithm:

1. Choose number of bootstrap sample sets

2. Choose sample size

3. Draw an observation from the original data set and replace it

4. Calculate the statistic (mean, standard error, etc.) on the sample

5. Take the average of the calculated statistics from part 4

```{r}
require(boot)
set.seed(1)
alpha.fn<-function(data,index){
 val <-mean(data[index,])
 return(val)
}
boot=boot(Boston$medv, alpha.fn,R=500)
```

#### d. Based on your bootstrap estimate from (c), provide a 95% confidence interval (CI) for the mean of `medv`. Compare it to the results obtained using `t.test(Boston$medv)`.

```{r}
```

#### e. Based on the data set, provide an estimate of the median value of `medv` in the population.

```{r}
```

#### f. We would like to estimate the standard error of the population median of `medv`. Unfortunately, there is no simple formula for computing the standard error of the median. Instead, estimate the standard error of the median using the bootstrap. Comment on your findings.

```{r}
```

#### g. Based on the data set, provide an estimate for the tenth percentile of `medv` in Boston suburbs.

```{r}
```

#### h. Use the bootstrap to estimate the standard error of the tenth percentile of `medv`. Comment on your findings.

```{r}
```

