---
title: "Chapter 3 Problem 13"
author: "Andira Putri"
output: pdf_document
---

#### In this exercise, you will create some simulated data and will fit simple linear regression models to it.

*Note - When working on problems that uses randomly-generated data sets, set.seed() reproduces the exact
same set of random numbers. This ensures consistent results.

#### a. Using the rnorm() function, create a vector x containing 100 observations drawn from a N(0,1) distribution. This represents a feature, X.

```{r}
set.seed(1)
x=rnorm(100,0,1)
```

#### b. Using the rnorm() function, create a vector eps containing 100 observations drawn from a N(0,0.25) distribution.

```{r}
eps=rnorm(100,0,0.25)
``` 

#### c. Using x and eps, generate a vector y according to the model Y=-1+0.5X+??. What is the length of vector y? What are the values of the coefficients in the model?

```{r}
y=0.5*x-1+eps
length(y) #length of y vector
```

$\beta_0=-1$ and $\beta_1=0.5$.

#### d. Create a scatterplot displaying the relationship between x and y.

```{r}
plot(x,y)
```

#### e. Fit a least squares model to predict y using x. Comment on the model obtained. How do the estimated coefficients compare to those in part c?

```{r}
lm.fit=lm(y~x)
summary(lm.fit)
```

The model suggests a strong relationship between x and y. The estimated coefficients are quite close to the actual $\beta_1$ and $\beta_0$ values in part c.

#### f. Display the least squares and population regression line on the scatterplot in part d.

```{r}
plot(x,y)
abline(-1,0.5,col="green",lwd=2) #population
abline(lm.fit,col="red",lwd=3) #least squares
legend("topleft",c("Population","Least Squares"),col=c("green","red"),lty=c(1,1))
```

#### g. Now fit a polynomial regression model that predicts y using x and x^2. Is there evidence that the quadratic term improves the model fit?

```{r}
lm.fitpoly=lm(y~x+I(x^2))
summary(lm.fitpoly)
```

There is no evidence suggesting that the quadratic term improves the model fit, given its high p-value