---
title: "Chapter 3 Problem 8"
author: "Andira Putri"
output: pdf_document
---

####

#### a. Use the lm() function to perform a simple linear regression with mpg as the response and horsepower as the predictor. Comment on the output.

```{r}
library(ISLR)
lm.fit=lm(mpg~horsepower,data=Auto)
summary(lm.fit)
```

* Relationship between predictor and response?

$H_o$: No relationship between horsepower & mpg. vs. $H_a$: There is a relationship between horsepower & mpg.

We reject the null hypothesis. The low p-value associated with the horsepower parameter ($\beta_1$) suggests that there is a relationship between horsepower and mpg.

* How strong is the relationship between the predictor and the response?

r = sqrt(0.6059) = 0.7784

The correlation coefficient indicates a strong relationship, though not conventionally the strongest.

* Is the relationship between the predictor and the response positive or negative?

There is a negative relationship. With a one-unit increase in horsepower, mpg decreases by 0.1578.

* What is the predicted mpg with a horsepower of 98? What are the associated 95% CI and PI?

Our model is: mpg = 39.9359 - 0.1578(horsepower)

39.9359 - 0.1578(98) = 24.4715.


```{r}
predict(lm.fit, data.frame(horsepower=c(98)),interval="confidence") #CI
predict(lm.fit, data.frame(horsepower=c(98)),interval="prediction") #PI
```


#### b. Plot the response and the predictor. Use the abline() function to display the least squares regression line.

```{r}
plot(Auto$horsepower,Auto$mpg,xlab="horsepower",ylab="mpg")
abline(lm.fit,lwd=3,col="blue")
```

#### c. Use the plot() function to produce diagnostic plots of the least squares regression fit. Comment on any problems you see with the fit.

```{r}
plot(lm.fit)
```

From the Residuals vs. Leverage plot, we see that there are some high leverage points (94, 117). The Residuals vs. Fitted plot follows a quadratic pattern, which could suggest non-linearity